Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-08 be.tex
zetaCrit plot

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value $\zeta_c$ of the wind heating parameter
  $\zeta \equiv \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of the flow $\mathcal{B}$ is positive near the break radius for some value of $\rs$, calculated for core ($\Gamma=0.1$)
  galaxies using equation~\eqref{eq:enthAnal}.. {\emph Bottom Panel:} Minimum value of the stagnation radius for which $\mathcal{B} > 0$ at the break radius as a function of $\zeta/\zeta_c < 1$, again calculated for core galaxies ($\Gamma=0.1$).}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{zetaCrit.pdf}
\caption{\label{fig:zetaCrit} {\emph Top panel:} Critical value
  $\zeta_c$ of the wind heating parameter $\zeta \equiv
  \sqrt{1+(v_w/\sigma_0)^2}$ above which the Bernoulli parameter of
  the flow $\mathcal{B}$ is positive near the break radius for some
  value of $\rs$, calculated for core ($\Gamma=0.1$, dot-dashed line)
  and cusp ($\Gamma=0.8$, solid line) galaxies using
  equation~\eqref{eq:enthAnal}.. {\emph Bottom Panel:} Minimum value
  of the stagnation radius for which $\mathcal{B} > 0$ at the break
  radius as a function of $\zeta/\zeta_c < 1$. }
\end{figure}
